### 2016-06-16 ch01-intro/introduction.tex
Some notes Tomas McKelvey

\paragraph{Select a model structure}
Once an experiment has been performed, the obtained input-output data are to be processed.
In many cases, the eventual goal of identification is to obtain a parametric model, so the user has to select a model structure and complexity based on both his prior knowledge and on the data.
A useful tool to help choose the model structure and/or model orders, is to inspect a nonparametric model of the system.
One such tool is the frequency response function.
For instance, by inspecting a frequency response function, a control engineer can have a rough idea of the system behavior in term of  approximate resonance frequencies, asymptotic slopes, \latin{etc.}
This gives a qualitative view of the minimally required complexity of the model and is hence a useful diagnostic tool.
However, since most parametric estimators enforce very little prior knowledge about the system, noise in the measurements can sometimes be a problem to distinguish the actual system features.

@@

In this dissertation, we focus on developing system identification techniques that are `user-friendly'.
The availability of easy to use and fast methods has been underlined by \citet{Gevers2011Challenges}.
In this context, `user-friendly' should be understood as having a good user experience for two groups of users:
\begin{itemize}
  \item novices, without formal training in system identification, optimization, \ldots and,
  \item well-seasoned identification practitioners that are already able to build good models.
\end{itemize}
Concretely, for novice users it is important to have straightforward techniques that require little interaction.
In practice, this boils down to methods that work well for a wide class of systems.
As such, only very generic assumptions of the system under test should be made and these should be easy to interpret.

>>>>

\paragraph{Select a model structure}
Once an experiment has been performed, the obtained input-output data are to be processed.
In many cases, the eventual goal of identification is to obtain a parametric model, so the user has to select a model structure and complexity based on both his prior knowledge and on the data.
A useful tool to help choose the model structure and/or model orders, is to inspect a nonparametric model of the system.
One such tool is the frequency response function.
For instance, by inspecting a frequency response function, a control engineer can have a rough idea of the system behavior in term of  approximate resonance frequencies, asymptotic slopes, \latin{etc.}
This gives a qualitative view of the minimally required complexity of the model and is hence a useful diagnostic tool.
However, since most nonparametric estimators enforce very little prior knowledge about the system, noise in the measurements can sometimes be a problem to distinguish the actual system features.

@@

In this dissertation, we focus on developing system identification techniques that are `user-friendly'.
The availability of easy to use and fast methods has been underlined by \citet{Gevers2011Challenges}.
In this context, `user-friendly' should be understood as having a good user experience for two groups of users:
%TODO: more groups ("two groups")
\begin{itemize}
  \item novices, without formal training in system identification, optimization, \ldots and,
  \item well-seasoned identification practitioners that are already able to build good models.
\end{itemize}
Concretely, for novice users it is important to have straightforward techniques that require little interaction.
In practice, this boils down to methods that work well for a wide class of systems.
As such, only very generic assumptions of the system under test should be made and these should be easy to interpret.
